### 2011-05-10 htdocs/user.tex
Added new instructions for walls in user guide
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1349 40876441-3496-0410-a613-a2fca35b2ae2

The boundary walls are switched on via the keyword value pair

\inputkey{boundary\_walls\_on [no | yes]}

If \texttt{yes} then the geometry is specified with the keyword
as one of

\inputkey{periodicity [1\_1\_1 | 1\_1\_0 | 1\_0\_0 | 0\_0\_0]}

Note that these are the only valid selections. \texttt{1\_1\_0}
gives periodic boundaries in the $x-$ and $y-$directions, with
walls at either edge in the $z-$direction. \texttt{1\_0\_0}
gives periodic conditions in the $x-$ direction only, while
\texttt{0\_0\_0} is a fully enclosed box.

In the case of the slab geometry, two further values are used so
that shear may be imparted to the system:

@@

These values set the $x-$component of the wall velocity at
$z = z_{min}$ and $z = z_{max}$, respectively. Like all
velocities, these values must respect the low Mach number
constraint $u_x < c_s$.

>>>>

The boundary walls are switched on via the keyword

\inputkey{boundary\_walls}

and with a complementatary specification of the key \texttt{periodicity}.

For example, walls at $x = x_{\min}$  and $x = x_{\max}$  are specified
by

\inputkey{boundary\_walls 1\_0\_0}

\inputkey{periodicity 0\_1\_1}

Both must be present. Note that there are a number of constraints on
valid choices, and the code will stop if there is an invalid choice, or
the two keys above do not match. Common choices are:
\texttt{boundary\_walls 0\_0\_1},
which gives periodic boundaries in the $x-$ and $y-$directions, with
walls at either edge in the $z-$direction; \texttt{0\_1\_1}
gives periodic conditions in the $x-$ direction only, while
\texttt{1\_1\_1} is a fully enclosed box.

In the case of the slab geometry with walls at $z = z_{\min}$ and
$z= z_{\max}$ (only),
two further values are used so that shear may be imparted to the system:

@@

These values set the $x-$component of the wall velocity at
$z = z_{\min}$ and $z = z_{\max}$, respectively. Like all
velocities, these values must respect the low Mach number
constraint $u_x < c_s$.
